Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-08-24 ms_pre_post.Rmd
Add cost section to the Model

We track interactions among discrete individuals in a small focal population that persists over multiple generations. Individuals within this population are either female or male, and are potentially related if they share a common ancestory. We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie]. At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding. The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$). A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates. Similarly, after mating has occurred, fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$. After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults. After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity. Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.

@@

Results
------------------------------------------------

>>>>

We track interactions among discrete individuals in a small focal population that persists over multiple generations. Individuals within this population are either female or male, and are potentially related if they share a common ancestory. We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie]. At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding. The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$). A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates. Similarly, after mating has occurred, post-copulatory fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$. After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults. After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity. Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.

Costs
----------------------------------------------

Values of phenotypic traits for tendency to engage in polyandry ($P_{p}$), mating ($M_{p}$), and fertilistation ($F_{p}$) each have costs, which independently increase the probability of a focal female's reproductive failure. These costs are all expressed prior to mating. In the case of tendency to engage in polyandry and inbreeding mating strategy, costs of $P_{p}$ ($c_{P}$) and $M_{p}$ ($c_{M}$) are interpreted biologically as costs associated with mate searching. In the case of inbreeding fertilisation strategy, the cost of $F_{g}$ is interpreted as an energetic cost associated with the physiological or biochemical mechanisms that need to be developed to bias fertilsation for inbreeding avoidance or inbreeding preference. Each cost independently increases the risk of female pre-mating mortality and, because generations are non-overlapping, total reproductive failure as a linear function of its associated trait. The probability that a focal female dies before mating due to the cost of polyandry is therefore $P_{p} \times c_{P}$. Similarly, the probability of pre-mating female mortality due to the cost of mating strategy and fertilisation strategy is $|M_{p}| \times c_{M}$ and $|F_{p}| \times c_{F}$, repectively, where $|M_{p}|$ is the absolute value of $M_{p}$ and $|F_{p}|$ is the absolute value of $F_{p}$. Absolute values are used for applying costs to inbreeding strategies because both negative and positive $M_{p}$ and $F_{p}$ bias breeding interactions with respect to kinship, while only positive values of $P_{p}$ affect a female's tendency for polyandry; zero and negative $P_{p}$ values always translate to monandrous phenotypes (see below).

Polyandry
----------------------------------------------

@@

Results
===================================================
